\textbf{On the (non-)exhaustivity of naturally occurring \whqs}

### 2022-11-13 papers/article/main.tex
main.text

% \begin{Center}
\noindent \textbf{Abstract}\\
\noindent Asking and answering questions is a staple of human communication. In order to answer a question effectively, a hearer must interpret the speaker's intention given the specific question asked. \emph{Wh}-questions like \emph{Where can I get coffee?} are underspecified for (non-)exhaustivity, i.e., how many answers must be provided to resolve the speaker's goal. Intuitions from the semantic literature report that questions are generally exhaustive, and non-exhaustive only in the context of specific linguistic factors (e.g., the modal \emph{can}, certain \emph{wh}-words). To test these assumptions, we collected question paraphrase ratings for naturally occuring root questions in variable linguistic contexts. In contrast to previous claims, we find that questions are not biased for exhaustivity. However, other prior observations are supported by the data. We argue that a full account of the observed distribution of meanings must integrate discourse factors like the hearer's estimate of the speaker's goal, alongside (or subsuming the effect of) linguistic cues.\\

\noindent \textbf{Keywords:} 
psycholinguistics; experimental pragmatics; corpus linguistics; \emph{wh}-questions; exhaustivity
% \end{Center}

@@

A root \whq can be answered in multiple ways. 
% \vspace{-.3cm}
\begin{exe}
    \ex {}
    \begin{xlist}
        \ex Where can I find coffee? \label{coffee1}
        % \vspace{-.1cm}
        \ex Who came to the party? \label{party}
    \end{xlist}
\end{exe}
% \vspace{-.3cm}
The most natural way to answer (\ref{coffee1}) is to mention a nearby coffee shop, while the most natural way to answer (\ref{party}) is to provide an exhaustive list of party-goers. That is, out of the blue, (\ref{coffee1}) receives a \emph{non-exhaustive} interpretation, while (\ref{party}) receives an \emph{exhaustive} one. We refer to these readings as `Mention-Some' (MS) and `Mention-All' (MA), respectively \cite<following> {hintikka1976,groenstok1982,groenstok1984}. MS and MA are also available as possible readings of embedded \whqs$\!$:
\begin{exe}
    \ex {}
    \begin{xlist}
        \ex Scully knows where I can find coffee. \label{emb_coffee1}
        % \vspace{-.1cm}
        \ex Scully knows who came to the party. \label{emb_party}
    \end{xlist}
\end{exe}
(\ref{emb_coffee1}) is true if Scully knows an MS answer to the root question (\ref{coffee1}), while (\ref{emb_party}) is true if Scully knows an MA answer to the root question (\ref{party}). On the surface, \whqs do not specify whether they are intended to be MS or MA. What makes (\ref{coffee1}) and (\ref{emb_coffee1}) naturally MS, and (\ref{party}) MA? 
% The answer to that question is the focus of this paper. \jd{we don't provide a full answer, so might have to weaken} 
In this research, we offer a contribution to answering that question by looking at the distribution of MS and MA interpreatations in naturally-occurring \whqs$\!$.

@@

% The picture that emerges is that there is considerable variation in \whq interpretation. That variation is the result of (1) inferred contextual goals of the speaker \jd{do we test this explicitly? how? here we should really only list what there is hard evidence for, and not speculation}, (2) the uttered question \jd{do you mean linguistic surface features? if so, say so}, (3) the hearer's inferences about the two \jd{how are the inferences different from the factors? probably delete this point, unless you quantify the inference separately in some way?}, and (4) any prior expectations that the hearer might have about either (1), (2), or (3) \jd{again, is this speculation based on individual examples cherry-picked at the end? or is this a clear empirical result? it's fine to just discuss these issues at the end, or foreshadow that you'll discuss them, but avoid presenting things as fact that aren't}. Together, with a more qualitative analysis of the contribution of the preceeding discourse context we argue that accounting for \whq meaning in terms of MA , or in terms of exceptional linguistic forms \jd{what is "accounting for \whq meaning in terms of MA, or in terms of exceptional linguistic forms" supposed to mean? vague.}, ignores important generalizations about non-linguistic information.

@@

The theoretical landscape with regards to the semantics/pragmatics of \whqs is highly disputed, and it raises theoretical and empirical issues that extend farther beyond the topic of \whqs. There are consistent empirical observations which can and are explained in theoretically conflicting ways; even the data themselves are questioned. That makes a straghtforward disucssion--and theory testing--approach difficult, to say the least.

@@

With that being said, we can say that there are two simple ways to approach MS: either it is semantic or it is pragmatic. Semantic treatments aruge that there is an underlying semantic explanation for MS, in other words that MS is grammatically licensed. In contrast, pragmatic accounts argue that pragmatic factors explain MS. This is a classic juxtaposition.

What are pragmatic factors? For Karttunen and Groenendijk \& Stokhof, it means a non-truth conditional process that determines what counts as a good answer (see, \citeA{karttunen1977} footnote 4; \citeA{groenstok1984} footnote 14 and discussion pp. 533). This understanding of ``pragmatic'' is maintained in \citeA{george2011} and indirectly in \cite{xiang2016} in the form of arguments against embedded ``pragmatic'' MS. The idea is that what counts as a good answer depends on the speaker/hearer interests, and in the embedded case, this information cannot penetrate grammatical structure. For Asher \& Lascarides and Ginzburg, ``pragmatic'' implies information about a conversational participant's beliefs/cognitive state, and goals/plans \cite<seee discussion on pp. 266 of>{asherlascarides1998}. The difference between these two perspectives is whether this pragmatic information has truth-conditional repurcussions; whether this information is available to the internal knowledge representations involved.

The problem here, is that drawing the line based on truth-conditional effects doesn't actaully aid either the empirical or theoretical situation. This is because of context-sensitivity.

% Let's look at analogy from a different field. It was long assumed that humans made (economic) decisions following the mathematical tenents of probability theory. The field of Behavioral Economics arose exactly because there was a discrepancy in the data: probablilty theory predicted

Drawing a distinction in this way confounds two separate perspectives on language \emph{understanding} and linguistic theory. Both present useful insights into how a \emph{hearer} determines the meaning of a \whq, but crucially make different assumptions about both theory and data. By introducing these perspectives, we will provide a frame in which to elaborate on our own view on MS and \whqs.

In his 1992 book \emph{Arenas of Language Use}, Clark described two approaches to linguistic inquiry: the language as \emph{product} approach and the language as \emph{action} approach. Product traditions view the sentence as a basic unit, an abstract representation produced by a grammar. In the realm of semantics, a semantic theory follow the product tradition, abstracting away as much as possible from any circumstantial or indexical information. Groenendijk \& Stokhoff allude to this in footnote 14 of the 1984 joint-dissertation, which describes their motivation for the semantics/pragmatics divide that they assume. Additionally, this thinking seems to underly George's rejection of a van Rooij style semantic theory, which supposedly gives up simplicity for incorporating more contextual/intentional/mental state information into the semantic theory (discussion on p.205). Often, such contextual information is acknowledged as playing a role in language production and comprehension, but then disregarded as playing a role in determining the truth (or answerhood) conditions of \whqs. It has often gone hand-in-hand with the idea that pragmatic information cannot ``interfere'' with semantics, and thus the prediction that MS should not occur in (at least some) embedded questions--see also \citeA<footnote 4>{karttunen1977}, and \cite{xiang2016}\mm{page number}.

@@

In this work, we adopt the perspective of the langauge as action tradition. Our guiding inquiry, then, concerns the \emph{interpretation} of \whqs, which happens by necessity in fixed naturalistic contexts, with conversational agents present, and actively engaged (presumably) in cognitive processes like mind-reading/intention-recognition. We will treat semantic theories as presenting minimal models of the conditions on interpretation. The linking assumption is that, if a theory puts a mechanism in the semantics, the reason is because that mechanism is by hypothesis part of the basic meaning of the linguistic item in question. Thus, by convention, this predicted semantic component presumably should be borne out more often than not empirically---that is, in the interpretations that na\"ive language users access on average. The behavioral patterns that we see in na\"ive language users should reflect the presence of the hypothesized mechanism.

With these comments in mind, we turn to the behavioral patterns that the semantic theories above predict when it comes to \whq interpretation.

In the following sections, we discuss the approaches to MS, and in the process identify four critical observations about factors that modulate the interpretation of MS, and \whqs generally. These four factors have served differentially as evidence for semantic and pragmatic accounts of MS, thus our discussions of theory will be tied up with the evidence that has been produced in support of those theories. To preview, the effect of existential (modal) force, and matrix question-embedding verbs will unroll in the section on semantic theories of MS; while the effects of \whw and contextual discourse goals will be discussed in the section on pragmatic approaches.

@@

Many researchers have implicity assumed that MS is more limited in distribution than MA, assuming that the predominant reading/answer is MA in most cases. As a result, many have maintained theories which posit only an underlying MA semantic representation usually based off \citeA{karttunen1977} or \citeA{groenstok1982,groenstok1984}. Some places where this view is explicitly stated \cite[Ch.6]{groenstok1982,groenstok1984,karttunen1977,vanrooij2003,nicolae2014,fox2014,xiang2016,dayal2016,george2011}.\mm{xiang2020,fox2018}.

@@

Thus, if the bare semantic contribution of a \whq is MA, then on average, we should find MA interpretations rated higher than MS interpretations. Additionally, we should find that MA interpretations will persist (or even increase) reqardless of whether contextual information is provided.
% \mm{review bernhard schwarz 2017 paper}

@@

Restricted ambiguity theories like \citeA[Ch. 6]{fox2014,nicolae2014,xiang2016,george2011}\mm{fox2018, xiang 2020} posit ambiguity in a subset of \whqs$\!$. Consider the examples below. 
\begin{exe}
\ex {} \label{exitentials}
    \begin{xlist}
        \ex Scully knows where I \textbf{can} find coffee.
        \ex Scully knows where \textbf{to find} coffee.
        \ex Scully knows where \textbf{a pen} is.
        \ex Scully knows who has \textbf{a light}.
        % \ex Scully knows what is a common Russian name.
        \ex Scully knows who some of the people at the party are.
    \end{xlist}
\end{exe}
What these examples have in common is that they involve an existential element: (a) and (b) have either an overt (a) or covert (b) modal \cite{bhatt1999,dayal2016,xiang2016,george2011,nicolae2014,fox2014}; (c) and (d) have an existential indefinite \cite{groenstok1982, groenstok1984,vanrooij2003,vanrooij2004} \mm{chierchia 2013? roelofsen and IS people }; and (e) has an existential quantifier. Motivated by the observation that MS consistently correlates with the presence of some kind of existential item, these researchers have argued that only \whqs with such elements are semantically ambiguous \cite[Ch:6]{nicolae2014,fox2014,xiang2016,george2011}\mm{fox2018, xiang 2020}. Without going in to too much detail, the common theoretical explanation for why these kinds of \whqs are ambiguous is because the existential element enters into a scope ambiguity with another element or operator in the question. Thus, our second prediction about the distribution of MS/MA is that modal questions will be MS biased, but non-modal questions will not be.

@@

\begin{tcolorbox}[colback=white]
\noindent \textbf{Prediction 2: Modal MS bias}.\\
Modal questions will give rise to MS on average more than non-modal questions. Non-modal questions will show an MA bias.
\end{tcolorbox}
\mm{Non-modal prediction is For Judith to smooth out so it doesn't sound like we're firing (too many) shots. tho it continues to be annoying going through all the quotes where these people EXPLICITLY say this, and then be told by them that I'm being unfair in my interpretation of the lit....}
We've included in this prediction that non-modal questions should exhibit an MA bias. On the one hand, this prediction seems perfectly reasonable for semantic theories on which MS is semantic only in virtue of the modal, becuase these theories posit mandatory covert exhaustivity operators that presumably render question MA in the absense of the crucial existential modal, ceterus peribus. This interpretation of the literature has supported explicitly in several places (\mm{Nicolae (2013), p.17, Fox 2018 in section 4 (pdf p.12) and Xiang, under review paper, pp.16}). However, some have objected to this interpretation of these theories, suggesting that questions should be examined on a case-by-case-basis (Xiang, p.c, Spector p.c.).

@@

These generalizations have more recently been called in to question both theoretically and experimentally \cite{cremchem2016,cremchem2017,klineroth2011,theiler2014} \mm{uegaki Sudo 2020}. Experimental work by Cremers and Chemla found non-strongly exhaustive readings with \emph{know-who} questions \cite{cremchem2016}, as well as strongly exhaustive readings with emotive factives like \emph{surprise} \cite{cremchem2017}. Note that this flexibility revealed experimentally is compatible with the flexibility we have already seen with the \emph{know-wh} reports in (\ref{exitentials}a-c) which are acceptable on MS readings. However, these studies did not address the availability of MS. Experimental results looking specifically at MS, \citeA{moyersyrett2019} did find differences between \emph{know-wh} and \emph{predict-wh}, where MS was more acceptable with the latter than the former. However, when discourse goals were systematically manipulated, even constructions with \emph{know} were acceptable on MS readings.

@@

For example, in a now classic discussion, \cite{groenstok1982,groenstok1984} present (\ref{news}) as evidence that MS requires special licensing from ``background concerns,'' \cite[p.543]{groenstok1984}.
\begin{exe}
    \ex Where do they sell Italian newspapers in Amsterdam? \label{news}
\end{exe}
The scenario that first comes to mind is that of an Italian tourist looking for word of their homeland, in which case the MS interpretation is the most natural. The ``background concern'', or \emph{goal}, of the questioner is to acquire the newspaper. However, the same question asked by a newspaper distributor interested in learning about the possible locations to distribute Italian newspapers for profit makes MA most natural. G\&S would arugment that, while the semantic contribution of the question is MA, the background concerns permit the acceptability of an MS answer only \emph{in an MS context}.
% They discussed a pragmatic and a semantic treatment, but dismiss the latter (see \cite{groenstok1984} Section 5, pp. 528-546 for the full discussion).

Other researchers have taken such data as evidence for different analyses of the underlying semnatic representation, presenting semantic theories that include variables parameterized to aspects of context \cite{boerlycan75,ginzburg1995,asherlascarides1998,lahiri2002,vanrooij2003,vanrooij2004}\mm{boer and lycan 1985}. The resolution of these variables crucially involves fixing certain apects of the speaker's beliefs and goals/plans. To prime the intuition, Asher \& Lascarides consider the following example:
\begin{exe}
    \ex 
    \begin{xlist}
        \ex Mulder: How do I get to the burried treasure?
        \ex Scully: You go to the secret island.
        \ex Mulder: Scully knows/told me how to get to the burried treasure.
    \end{xlist}
\end{exe}
Regardless of (b) being an answer to (a) in the standard sense, whether or not Mulder's statement in (c) is true will \emph{also} depend on what his goals are, and whether he knows first how to get to the secret island. If he needs to get to the burried treasure but does not have that prerequisite knowledge, then (c) is judged to be false. Thus, even the truth of (c) crucially depends on the speaker's plan and cognitive state.

@@

% \mm{REDUNDANT? These issues all essentially revolve around resolving the reference of the \emph{wh}-domain. First, context determine the elements in the set being quantified over, i.e., that \emph{Where are we?} is restricted to a set of places that is contextually salient. This is normal, and happens with quantifiers more generally (see e.g., \cite{lasersohn1999} and \mm{roelof, groenen, ciardelli 2018}. Sometimes this is discussed as implicit domain restriction (\cite{vonfintel1994}), the phenomenon by which a quantified NP like \emph{everyone} doesn't quantify over everyone in the entire universe, but over a set that's already been restricted (see e.g., discussions in \mm{zimmermann 2010}, \cite{george2011}, \mm{fox 2018}. On Von Fintel's account, restriction occurs when the immediately preceeding discourse includes a noun phrase that serves as an available restrictor to the quantifier. However, in the case of \whqs (and even of wuantifiers), it's clear that such explicit NPs are not readily available, and restriction must appeal to the speaker's intentions.}

@@

Finally, there has been some discussion about the role that d-linking and number marking may play \cite{pesetsky1987,dayal1996,comorovski1996,xiang2016}\mm{comorovski 2006?, sirivastav 1991, }. \citeA{dayal2016} aruges convincingly that these facts can be overidden by context. Xiang \& Cremers (2017) tested the availability of MS in plural-marked \whqs like \emph{Mary remembers which children can lead the dance} as compared to \emph{Mary remember who can lead the dance}. In Experiment 1, they found no main effect of \whw or interaction with modality, while in Experiment 2 they only found a significant interaction with modality.

@@

Recent experimental work \cite{moyer2020,moyersyrett2019} has confirmed that the \whw does indeed modulate interpretation as predited by Ginzburg and Asher \& Lascarides: MS contexts were less acceptable for \emph{who}-questions than for \emph{where}-questions. At the same time, there was variation based on particular items suggesting that this variation in \whw is really tracking contextual modulation in how the \whw domain is fixed.

Thus, if non-\emph{who} questions require more contextual specification than \emph{who}-questions,

@@

Here we summarize the observations and predictions.
\begin{table}[h!]
    \centering
   \begin{tabular}{| p{0.25\linewidth} | p{0.6\linewidth} |}
    \hline
    {} & \textbf{Prediction} \\
    \hline
    \textbf{Overall} & On average, \whqs will be interpreted MA more than MS.\\
    \hline
    \textbf{Modality: Presence} & On average, modal questions will be interpreted MS.\\
    \textbf{Modality: Absence} & On average, non-modal questions will be interpreted MA. \\
    \hline
    \textbf{Matrix Verb} & On average, \emph{know-wh} will be interpreted MA.\\
    \hline
    \textbf{Wh-Word} & On average, \emph{who}-questions will be interpreted MA,\\
    {} & non-\emph{who}-questions will be interpreted MS.\\
    \hline
    \textbf{Discourse Goals} & MS/MA interpretations require crucial information provided by the discourse context.\\
    \hline
   \end{tabular}
    \caption{Summary of Main factors of influence on MS/MA interpretation, and the directionality of their predicted influence.}
    \label{fig:my_label}
\end{table}

@@

@@

\subsubsection{Cases with a big difference between the two studies}

>>>>

\small
\noindent \textbf{Abstract}\\
\noindent \mm{Asking and answering questions is a staple of human communication. In order to answer a question effectively, a hearer must interpret the speaker's intention given the specific question asked. \emph{Wh}-questions like \emph{Where can I get coffee?} are underspecified for (non-)exhaustivity, i.e., how many answers must be provided to resolve the speaker's goal. Intuitions from the semantic literature report that questions are generally exhaustive, and non-exhaustive only in the context of specific linguistic factors (e.g., the modal \emph{can}, certain \emph{wh}-words). To test these assumptions, we collected question paraphrase ratings for naturally occurring root questions in variable linguistic contexts. In contrast to previous claims, we find that questions are not biased for exhaustivity. However, other prior observations are supported by the data. We argue that a full account of the observed distribution of meanings must integrate discourse factors like the hearer's estimate of the speaker's goal, alongside (or subsuming the effect of) linguistic cues.}\\

\noindent \textbf{Keywords:} 
experimental pragmatics; corpus linguistics; psycholinguistics; \emph{wh}-questions; non-exhaustivity; mention-some
\normalsize

@@

A root \whq can be answered in multiple ways. 
% \vspace{-.3cm}
\begin{exe}
    \ex {}
    \begin{xlist}
        \ex Where can I find coffee? \label{coffee1}
        % \vspace{-.1cm}
        \ex Who came to the party? \label{party}
    \end{xlist}
\end{exe}
% \vspace{-.3cm}
The most natural way to answer (\ref{coffee1}) is to mention a nearby coffee shop, while the most natural way to answer (\ref{party}) is to provide an exhaustive list of party-goers. That is, out of the blue, (\ref{coffee1}) receives a \emph{non-exhaustive} interpretation, while (\ref{party}) receives an \emph{exhaustive} one. We refer to these readings as `Mention-Some' (MS) and `Mention-All' (MA), respectively \cite<following> {hintikka1976,groenstok1982,groenstok1984}. MS and MA are also available as possible readings of embedded \whqs$\!$:
\begin{exe}
    \ex {}
    \begin{xlist}
        \ex Scully knows where I can find coffee. \label{emb_coffee1}
        % \vspace{-.1cm}
        \ex Scully knows who came to the party. \label{emb_party}
    \end{xlist}
\end{exe}
(\ref{emb_coffee1}) is true if Scully knows an MS answer to the root question (\ref{coffee1}), while (\ref{emb_party}) is true if Scully knows an MA answer to the root question (\ref{party}). On the surface, \whqs do not specify whether they are intended to be MS or MA. What makes (\ref{coffee1}) and (\ref{emb_coffee1}) naturally MS, and (\ref{party}) MA? 
% The answer to that question is the focus of this paper. \jd{we don't provide a full answer, so might have to weaken} 
In this research, we offer a contribution to answering that question by looking at the distribution of MS and MA interpretations in naturally-occurring \whqs$\!$.

@@

% The picture that emerges is that there is considerable variation in \whq interpretation. That variation is the result of (1) inferred contextual goals of the speaker \jd{do we test this explicitly? how? here we should really only list what there is hard evidence for, and not speculation}, (2) the uttered question \jd{do you mean linguistic surface features? if so, say so}, (3) the hearer's inferences about the two \jd{how are the inferences different from the factors? probably delete this point, unless you quantify the inference separately in some way?}, and (4) any prior expectations that the hearer might have about either (1), (2), or (3) \jd{again, is this speculation based on individual examples cherry-picked at the end? or is this a clear empirical result? it's fine to just discuss these issues at the end, or foreshadow that you'll discuss them, but avoid presenting things as fact that aren't}. Together, with a more qualitative analysis of the contribution of the preceding discourse context we argue that accounting for \whq meaning in terms of MA , or in terms of exceptional linguistic forms \jd{what is "accounting for \whq meaning in terms of MA, or in terms of exceptional linguistic forms" supposed to mean? vague.}, ignores important generalizations about non-linguistic information.

@@

The theoretical landscape with regards to the semantics/pragmatics of \whqs is highly disputed, and it raises both theoretical and empirical issues that extend beyond the topic of \whqs. There are consistent empirical observations which can and are explained in theoretically conflicting ways; even the data themselves are questioned. That makes a straightforward discussion--and theory testing--approach difficult, to say the least.

@@

With that being said, we can say that there are two simple classic ways to approach MS: either it is semantic or it is pragmatic. Semantic treatments aruge that there is an underlying semantic explanation for MS, in other words that MS is grammatically licensed. In contrast, pragmatic accounts argue that pragmatic factors explain MS. This is a classic juxtaposition.

What are the pragmatic factors in this case? Looking first at the literature, for Karttunen and Groenendijk \& Stokhof, it means any non-truth conditional process that determines what counts as a good answer to a root question (see, \citeA{karttunen1977} footnote 4; \citeA{groenstok1984} footnote 14 and discussion pp. 533). This understanding of ``pragmatic'' is maintained in \citeA{george2011} and indirectly in \cite{xiang2016} in the form of the reiteration of arguments against embedded ``pragmatic'' phenomenon. The idea is that what counts as a good answer depends on the speaker/hearer interests, which permits a answerer/hearer to be a little less rigorous in terms of their standards for truthfulness (or answerhood for root questions). For Asher \& Lascarides and Ginzburg, ``pragmatic'' implies information about a conversational participant's beliefs/cognitive state, and goals/plans \cite<seee discussion on pp. 266 of>{asherlascarides1998}.

These two sides share the belief about what is involved in pragmatic information, but they differ in terms of their underlying beliefs about how that information interacts with linguistic structure. The difference between these two perspectives is whether this pragmatic information has truth-conditional repercussions; whether this information is available to the internal knowledge representations involved. In particular, on a Karttunen/Groenendijk \& Stokhof kind of theory (we can think of this as being a mainstream semantic theory) pragmatic information is not available sub-sententially. Processes integrating pragmatic information take as input a full sentential-level meaning (something that has a truth value). %and derives, given the contextual/goal-relevant information (including speaker or conversational participants' mental states), a semi-true or almost-true proposition. 
In contrast, a theory like Asher \& Lascarides SDRT is designed exactly to include this kind of information in the compositional grammatical process. Drawing the line based on truth-conditional effects doesn't actually aid either the empirical or theoretical situation because the rampant context-sensitivity in natural language, as exemplified by \whqs, entails that meaning resolution (i.e., determining the truth-conditional content of a sentence) will depend on exactly that contextual information that is typically considered to indicate a pragmatic phenomenon.

% Here is perhaps a more useful distinction that will allow us to coherently discuss \whq interpretation in light of experimental data. This distinction

% Drawing a distinction in this way confounds two separate perspectives on language \emph{understanding} and linguistic theory. Both present useful insights into how a \emph{hearer} determines the meaning of a \whq, but crucially make different assumptions about both theory and data. By introducing these perspectives, we will provide a frame in which to elaborate on our own view on MS and \whqs.

In his 1992 book \emph{Arenas of Language Use}, Clark described two approaches to linguistic inquiry: the language as \emph{product} approach and the language as \emph{action} approach. Product traditions view the sentence as a basic unit, an abstract representation produced by a grammar. In the realm of semantics, a semantic theory follow the product tradition, abstracting away as much as possible from any circumstantial or indexical information. Groenendijk \& Stokhoff allude to this in footnote 14 of the 1984 joint-dissertation, which describes their motivation for the semantics/pragmatics divide that they assume. Additionally, this thinking seems to underly George's rejection of a van Rooij style semantic theory, which supposedly gives up simplicitly for incorporating more contextual/intentional/mental state information into the semantic theory (discussion on p.205). Often, such contextual information is acknowledged as playing a role in language production and comprehension, but then disregarded as playing a role in determining the truth (or answerhood) conditions of \whqs. It has often gone hand-in-hand with the idea that pragmatic information cannot ``interfere'' with semantics, and thus the prediction that MS should not occur in (at least some) embedded questions--see also \citeA<footnote 4>{karttunen1977}, and \cite{xiang2016}\mm{page number}.

@@

In this work, we adopt the perspective of the language as action tradition. Our guiding inquiry, then, concerns the \emph{interpretation} of \whqs, which happens by necessity in fixed naturalistic contexts, with conversational agents present, and actively engaged (presumably) in cognitive processes like mind-reading/intention-recognition. We will treat semantic theories as presenting minimal models of the conditions on interpretation. The linking assumption is that, if a theory puts a mechanism in the semantics, the reason is because that mechanism is by hypothesis part of the basic meaning of the linguistic item in question. Thus, by convention, this predicted semantic component presumably should be borne out more often than not empirically---that is, in the interpretations that na\"ive language users access on average. The behavioral patterns that we see in na\"ive language users should reflect the presence of the hypothesized mechanism.

With these comments in mind, in the following sections we discuss the approaches to MS, and in the process identify four critical observations about factors that modulate the interpretation of MS, and \whqs generally. These four factors have served differentially as evidence for semantic and pragmatic accounts of MS, thus our discussions of theory will be tied up with the evidence that has been produced in support of those theories. To preview, the effect of existential (modal) force, and matrix question-embedding verbs will unroll in the section on semantic theories of MS; while the effects of \whw and contextual discourse goals will be discussed in the section on pragmatic approaches.

@@

Many researchers have implicitly assumed that MS is more limited in distribution than MA, assuming that the predominant reading/answer is MA in most cases. As a result, many have maintained theories which posit only an underlying MA semantic representation usually based off \citeA{karttunen1977} or \citeA{groenstok1982,groenstok1984}. Some places where this view is explicitly stated \cite[Ch.6]{groenstok1982,groenstok1984,karttunen1977,vanrooij2003,nicolae2014,fox2014,xiang2016,dayal2016,george2011}.\mm{xiang2020,fox2018}.

@@

Thus, if the bare semantic contribution of a \whq is MA, then on average, we should find MA interpretations rated higher than MS interpretations. Additionally, we should find that MA interpretations will persist (or even increase) regardless of whether contextual information is provided.
% \mm{review bernhard schwarz 2017 paper}

@@

Restricted ambiguity theories like \citeA[Ch. 6]{fox2014,nicolae2014,xiang2016,george2011}\mm{fox2018, xiang 2020} posit ambiguity in a subset of \whqs$\!$. Consider the examples below. 
\begin{exe}
\ex {} \label{existentials}
    \begin{xlist}
        \ex Scully knows where I \textbf{can} find coffee.
        \ex Scully knows where \textbf{to find} coffee.
        \ex Scully knows where \textbf{a pen} is.
        \ex Scully knows who has \textbf{a light}.
        % \ex Scully knows what is a common Russian name.
        \ex Scully knows who some of the people at the party are.
    \end{xlist}
\end{exe}
What these examples have in common is that they involve an existential element: (a) and (b) have either an overt (a) or covert (b) modal \cite{bhatt1999,dayal2016,xiang2016,george2011,nicolae2014,fox2014}; (c) and (d) have an existential indefinite \cite{groenstok1982, groenstok1984,vanrooij2003,vanrooij2004} \mm{chierchia 2013? roelofsen and IS people }; and (e) has an existential quantifier. Motivated by the observation that MS consistently correlates with the presence of some kind of existential item, these researchers have argued that only \whqs with such elements are semantically ambiguous \cite[Ch:6]{nicolae2014,fox2014,xiang2016,george2011}\mm{fox2018, xiang 2020}. Without going in to too much detail, the common theoretical explanation for why these kinds of \whqs are ambiguous is because the existential element enters into a scope ambiguity with another element or operator in the question. Thus, our second prediction about the distribution of MS/MA is that modal questions will be MS biased, but non-modal questions will not be.

@@

\begin{tcolorbox}[colback=white]
\noindent \textbf{Prediction 2: Modal MS bias}.\\
Modal questions will give rise to MS on average more than non-modal questions. Non-modal questions will show an MA bias.
\end{tcolorbox}
\mm{Non-modal prediction is For Judith to smooth out so it doesn't sound like we're firing (too many) shots. tho it continues to be annoying going through all the quotes where these people EXPLICITLY say this, and then be told by them that I'm being unfair in my interpretation of the lit....}
We've included in this prediction that non-modal questions should exhibit an MA bias. On the one hand, this prediction seems perfectly reasonable for semantic theories on which MS is semantic only in virtue of the modal, because these theories posit mandatory covert exhaustivity operators that presumably render question MA in the absence of the crucial existential modal, ceterus peribus. This interpretation of the literature has supported explicitly in several places (\mm{Nicolae (2013), p.17, Fox 2018 in section 4 (pdf p.12) and Xiang, under review paper, pp.16}). However, some have objected to this interpretation of these theories, suggesting that questions should be examined on a case-by-case-basis (Xiang, p.c, Spector p.c.).

@@

These generalizations have more recently been called in to question both theoretically and experimentally \cite{cremchem2016,cremchem2017,klineroth2011,theiler2014} \mm{uegaki Sudo 2020}. Experimental work by Cremers and Chemla found non-strongly exhaustive readings with \emph{know-who} questions \cite{cremchem2016}, as well as strongly exhaustive readings with emotive factives like \emph{surprise} \cite{cremchem2017}. Note that this flexibility revealed experimentally is compatible with the flexibility we have already seen with the \emph{know-wh} reports in (\ref{existentials}a-c) which are acceptable on MS readings. However, these studies did not address the availability of MS. Experimental results looking specifically at MS, \citeA{moyersyrett2019} did find differences between \emph{know-wh} and \emph{predict-wh}, where MS was more acceptable with the latter than the former. However, when discourse goals were systematically manipulated, even constructions with \emph{know} were acceptable on MS readings.

@@

For example, in a now classic discussion, \cite{groenstok1982,groenstok1984} present (\ref{news}) as evidence that MS requires special licensing from ``background concerns,'' \cite[p.543]{groenstok1984}.
\begin{exe}
    \ex Where do they sell Italian newspapers in Amsterdam? \label{news}
\end{exe}
The scenario that first comes to mind is that of an Italian tourist looking for word of their homeland, in which case the MS interpretation is the most natural. The ``background concern'', or \emph{goal}, of the questioner is to acquire the newspaper. However, the same question asked by a newspaper distributor interested in learning about the possible locations to distribute Italian newspapers for profit makes MA most natural. G\&S would argue that, while the semantic contribution of the question is MA, the background concerns permit the acceptability of an MS answer only \emph{in an MS context}.
% They discussed a pragmatic and a semantic treatment, but dismiss the latter (see \cite{groenstok1984} Section 5, pp. 528-546 for the full discussion).

Other researchers have taken such data as evidence for different analyses of the underlying semantic representation, presenting semantic theories that include variables parameterized to aspects of context \cite{boerlycan75,ginzburg1995,asherlascarides1998,lahiri2002,vanrooij2003,vanrooij2004}\mm{boer and lycan 1985}. The resolution of these variables crucially involves fixing certain apects of the speaker's beliefs and goals/plans. To prime the intuition, Asher \& Lascarides consider the following example:
\begin{exe}
    \ex 
    \begin{xlist}
        \ex Mulder: How do I get to the buried treasure?
        \ex Scully: You go to the secret island.
        \ex Mulder: Scully knows/told me how to get to the buried treasure.
    \end{xlist}
\end{exe}
Regardless of (b) being an answer to (a) in the standard sense, whether or not Mulder's statement in (c) is true will \emph{also} depend on what his goals are, and whether he knows first how to get to the secret island. If he needs to get to the buried treasure but does not have that prerequisite knowledge, then (c) is judged to be false. Thus, even the truth of (c) crucially depends on the speaker's plan and cognitive state.

@@

% \mm{REDUNDANT? These issues all essentially revolve around resolving the reference of the \emph{wh}-domain. First, context determine the elements in the set being quantified over, i.e., that \emph{Where are we?} is restricted to a set of places that is contextually salient. This is normal, and happens with quantifiers more generally (see e.g., \cite{lasersohn1999} and \mm{roelof, groenen, ciardelli 2018}. Sometimes this is discussed as implicit domain restriction (\cite{vonfintel1994}), the phenomenon by which a quantified NP like \emph{everyone} doesn't quantify over everyone in the entire universe, but over a set that's already been restricted (see e.g., discussions in \mm{zimmermann 2010}, \cite{george2011}, \mm{fox 2018}. On Von Fintel's account, restriction occurs when the immediately preceding discourse includes a noun phrase that serves as an available restrictor to the quantifier. However, in the case of \whqs (and even of quantifiers), it's clear that such explicit NPs are not readily available, and restriction must appeal to the speaker's intentions.}

@@

Finally, there has been some discussion about the role that d-linking and number marking may play \cite{pesetsky1987,srivastav1991,dayal1996,comorovski1996,xiang2016}\mm{comorovski 2006?}. \citeA{dayal2016} aruges that these facts can be overridden by context. \citeA{xiangcremers} tested the availability of MS in plural-marked \whqs like \emph{Mary remembers which children can lead the dance} as compared to \emph{Mary remember who can lead the dance}. In Experiment 1, they found no main effect of \whw or interaction with modality, while in Experiment 2 they only found a significant interaction with modality.

@@

Recent experimental work \cite{moyer2020,moyersyrett2019} has confirmed that the \whw does indeed modulate interpretation as predited by Ginzburg and Asher \& Lascarides: MS contexts were less acceptable for \emph{who}-questions than for \emph{where}-questions. At the same time, there was variation based on particular items suggesting that this variation in \whw is really tracking contextual modulation in how the \whw domain is fixed. Thus, if non-\emph{who} questions require more contextual specification than \emph{who}-questions, we expect to see differences between the Conext and No Context tasks: participants should be more uncertain about the interpretation of non-\emph{who} than \emph{who} questions.

@@

Here we summarize the observations and predictions.
\begin{table}[h!]
    \centering
   \begin{tabular}{l p{0.25\linewidth} p{0.6\linewidth} }
    \toprule
    % {} & \textbf{Prediction} \\
    % \midrule
    \textbf{1} & Overall & On average, \whqs will be interpreted MA more than MS.\\
    \midrule
    \textbf{2} & Modal Present & On average, modal questions will be interpreted MS, while on average, non-modal questions will be interpreted MA.\\
    \midrule
    \textbf{3} & Matrix Verb & On average, \emph{know-wh} will be interpreted MA.\\
    \midrule
    \textbf{4} & Discourse Goals & MS requires information from the discourse context, without which it will be infelicitous\\
    \midrule
    \textbf{5} & Wh-Word & On average, \emph{who}-questions will be interpreted MA, non-\emph{who}-questions will be interpreted MS.\\
    \bottomrule
   \end{tabular}
    \caption{Summary of Main factors of influence on MS/MA interpretation, and the directionality of their predicted influence.}
    \label{fig:my_label}
\end{table}

@@

\bottomrule
\end{tabular} 
\end{center} 
\end{table}

@@

\subsubsection{Cases with a big difference between Context and NoContext Tasks}
